Dominance Regions for Imaginary $\bfg$-vectors

### 2021-08-23 dominance_regions.tex
Added some preliminary results on dominant Dyck paths

\documentclass{amsart}
\usepackage{amsmath,amssymb,latexsym,color}
\usepackage[margin=1in]{geometry}
\usepackage{tikz}
\usepackage[bookmarks=true, bookmarksopen=true, bookmarksdepth=3,bookmarksopenlevel=2, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, menucolor=blue, urlcolor=blue]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}{Question}

@@

\newcommand{\Aut}{\operatorname{Aut}}
\newcommand{\Col}{\operatorname{Col}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\Id}{\operatorname{Id}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\obeta}{{\overline{\beta}}}
\newcommand{\oi}{{\overline{\imath}}}
\newcommand{\ot}{{\overline{t}}}
\newcommand{\wt}{{\operatorname{wt}}}

@@

@@

  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by the following six inequalities:
  \begin{align}
    -\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1+\lambda_2-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
  \end{align}
  Are any of these better forms?
  \begin{align}
    (x-\lambda_1)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2)\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \nonumber \iff -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \nonumber \iff -b\lambda_2 + (x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+(x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \nonumber \iff c\lambda_1+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+b\lambda_2+(x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
  \end{align}
  Another proposal (I also changed the order of the equations)
  \begin{align}
    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq \frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 
    \\
    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
    \\
    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
    \\
    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1
    \\
    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
  \end{align}
  Maybe this one:
  \begin{align}
    (b c-\sqrt{b c (b c-4)})(x-\lambda_1)+2b(y-\lambda_2) & \geq0
    \\
    (b c+\sqrt{b c (b c-4)})(x-\lambda_1)-2b(y-\lambda_2) & \geq (b c+\sqrt{b c (b c-4)})b\lambda_2 
    \\
    -(b c-\sqrt{b c (b c-4)})(x-\lambda_1)-2b(y-\lambda_2)& \geq 2bc\lambda_1+(b c+\sqrt{b c (b c-4)})b\lambda_2
    \\
    -2c(x-\lambda_1)-(b c-\sqrt{b c (b c-4)})(y-\lambda_2)& \geq0
    \\
    2c(x-\lambda_1)-(b c+\sqrt{b c (b c-4)})(y-\lambda_2) & \geq -(b c+\sqrt{b c (b c-4)})c\lambda_1
    \\
    2c(x-\lambda_1)+(b c-\sqrt{b c (b c-4)})(y-\lambda_2) & \geq -(b c+\sqrt{b c (b c-4)})c\lambda_1-2cb\lambda_2
  \end{align}

@@

  \section{Ignore}
  Rank 4 Skew-Symmetric $B$

  $P(\lambda)=\lambda^4 + a\lambda^3 + b\lambda^2 + c\lambda + 1$

  \begin{align*}
    a
    &=-b_{41}b_{21}b_{32}b_{43}-b_{31}b_{21}b_{32}-b_{41}b_{21}b_{42}-b_{41}b_{31}b_{43}-b_{42}b_{32}b_{43}-b_{21}b_{21}-b_{31}b_{31}-b_{32}b_{32}-b_{41}b_{41}-b_{42}b_{42}-b_{43}b_{43}+4\\
    c
    &=-b_{21}b_{32}b_{43}b_{41}-b_{21}b_{32}b_{31}-b_{21}b_{42}b_{41}-b_{31}b_{43}b_{41}-b_{32}b_{43}b_{42}-b_{21}b_{21}-b_{31}b_{31}-b_{32}b_{32}-b_{41}b_{41}-b_{42}b_{42}-b_{43}b_{43}+4\\
    b
    &=b_{41} b_{32} b_{32} b_{41} - b_{31} b_{42} b_{32} b_{41} - b_{31} b_{43} b_{21} b_{42} - b_{41} b_{32} b_{31} b_{42} + b_{31} b_{42} b_{31} b_{42} + b_{21} b_{43} b_{21} b_{43} - b_{21} b_{42} b_{31} b_{43}\\
    &\quad - b_{21} b_{32} b_{31} - b_{31} b_{21} b_{32} - b_{21} b_{42} b_{41} - b_{31} b_{43} b_{41} - b_{32} b_{43} b_{42} - b_{41} b_{21} b_{42} - b_{41} b_{31} b_{43} - b_{42} b_{32} b_{43}\\
    &\quad - 2 b_{21} b_{21} - 2 b_{31} b_{31} - 2 b_{32} b_{32} - 2 b_{41} b_{41} - 2 b_{42} b_{42} - 2 b_{43} b_{43} + 6\\
    &=a+c-2+m\\
    &=a+c-2+n^2\\
    m
    &=b_{41}b_{21}b_{32}b_{43}+b_{21}b_{32}b_{43}b_{41}+b_{41}b_{32}b_{32}b_{41}-b_{31}b_{42}b_{32}b_{41}-b_{31}b_{43}b_{21}b_{42}-b_{41}b_{32}b_{31}b_{42}+b_{31}b_{42}b_{31}b_{42}+b_{21}b_{43}b_{21}b_{43}\\
    &\quad -b_{21}b_{42}b_{31}b_{43}\\
    &=(b_{31}b_{42}-b_{32}b_{41}-b_{21}b_{43})^2\\
    n
    &=b_{31}b_{42}-b_{32}b_{41}-b_{21}b_{43}\\
  \end{align*}

  Observe that $P(-1)=n^2$.
  What happens when $\lambda=\frac{-a\pm\sqrt{a^2-4}}{2}$?  You get $P(\lambda)=(b-2)\lambda^2$.

>>>>

\documentclass{amsart}
\usepackage{amsmath,amssymb,latexsym,color,ulem}
\usepackage[margin=1in]{geometry}
\usepackage{tikz}
\usepackage[bookmarks=true, bookmarksopen=true, bookmarksdepth=3,bookmarksopenlevel=2, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, menucolor=blue, urlcolor=blue]{hyperref}

\usepackage[draft]{say}
\newcommand{\sayDR}[1]{\say[DR]{\color{red}{\bf DR:}\;#1}}
\newcommand{\saySS}[1]{\say[SS]{\color{blue}{\bf SS:}\;#1}}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}{Question}

@@

\newcommand{\Aut}{\operatorname{Aut}}
\newcommand{\Col}{\operatorname{Col}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\Id}{\operatorname{Id}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\obeta}{{\overline{\beta}}}
\newcommand{\oi}{{\overline{\imath}}}
\newcommand{\ot}{{\overline{t}}}
\newcommand{\WA}{{W\!\!A}}
\newcommand{\wt}{{\operatorname{wt}}}
\newcommand{\Sh}{{\operatorname{Sh}}}

@@

  Our calculations reveal the maximal support possible for a pointed basis which reproduces under mutations.
  In particular, any candidate basis can be ruled out using these results based upon their support alone.

@@

  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by the following six inequalities:
  \begin{align}
    -\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1+\lambda_2-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
  \end{align}
  Are any of these better forms?
  \begin{align}
    (x-\lambda_1)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2)\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \nonumber \iff -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \nonumber \iff -b\lambda_2 + (x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+(x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \nonumber \iff c\lambda_1+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+b\lambda_2+(x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
  \end{align}
  Another proposal (I also changed the order of the equations)
  \begin{align}
    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
    \\
    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
    \\
    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
    \\
    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
    \\
    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
  \end{align}
  Maybe this one:
  \begin{align}
    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
    \\
    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
    \\
    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
    \\
    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
    \\
    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
  \end{align}

@@

  \section{Bases From Compatible Pairs on Dyck Paths}
  \sayDR{This is a bit of a repetition of the above introduction to Dyck paths, but with slightly different goals it seemed that a modified exposition was more appropriate.}
  For $a_1,a_2\in\ZZ_{\ge0}$, choose a Dyck path $D$ in the lattice rectangle $[0,a_1]\times[0,a_2]$.
  Consider $D$ as the set of its edges taken as a totally ordered set along the natural labeling from $(0,0)$ to $(a_1,a_2)$.
  It may be convenient to identify $D$ with the ordered set $[1,a_1+a_2]$.
  Write $D=D_1\sqcup D_2$, where $D_1$ is the set of horizontal edges and $D_2$ is the set of vertical edges.
  Clearly, $|D_1|=a_1$ and $|D_2|=a_2$.

  Write $D^{max}=D^{max}[a_1,a_2]$ for the maximal Dyck path in the lattice rectangle $[0,a_1]\times[0,a_2]$, i.e. $D^{max}$ never crosses above the diagonal line joining $(0,0)$ to $(a_1,a_2)$ and any lattice point above $D_{max}$ also lies above the diagonal.

  Observe that the data of $D$ is just the data of a bipartition of a finite totally ordered set $D=D_1\sqcup D_2$.

  For $e<e'\in D$, write $ee'$ for the subpath of $D$ beginning with $e$ and ending with $e'$.
  \begin{definition}
    A subset $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$ is \emph{compatible} if: for every $h\in H$ and $v\in V$ with $h<v$, there exists an edge $e\in hv$ such that one of the following conditions is satisfied
    \[e\ne v \quad \text{and} \quad |he\cap D_2|=c|he\cap D_1|\]
    \[e\ne h \quad \text{and} \quad |ev\cap D_1|=b|ev\cap D_2|\]
    Write $\cC_D$ for the collection of all compatible subsets of $D$.
  \end{definition}
  \begin{remark}
    In the construction of the greedy basis, it is necessary to consider $D$ as closed cycle by identifying $(0,0)$ with $(a_1,a_2)$ and allowing subpaths $ee'$ with $e'<e$ to ``wrap around'' $D$ in the obvious way.
    When we wish to emphasize that this condition should be imposed, we denote the Dyck path $D$ instead by $D_\WA$.
    For $(a_1,a_2)=(u_{m+1,+},u_{m,-})$ or $(u_{m,+},u_{m+1,-})$, the wrap around condition does not restrict compatibility and can thus safely be omitted.
  \end{remark}

  We associate to $D$ the element $x_D\in\ZZ_{\ge0}[x_1^{\pm1},x_2^{\pm1}]$ defined as follows
  \[x_D:=x_1^{-a_1} x_2^{-a_2} \sum_{H\sqcup V\in\cC_D} x_1^{b|V|} x_2^{c|H|}.\]

  \begin{theorem}[\cite{lee-li-zelevinsky}]
    For $(a_1,a_2)=(u_{m+1,+},u_{m,-})$ or $(u_{m,+},u_{m+1,-})$ for $m\ge0$, the element $x_D[a_1,a_2]$ is a non-initial cluster variable.
    Otherwise, the element $x_{D_\WA}$ is an element of the greedy basis
  \end{theorem}

  \begin{lemma}
    Suppose there are two factorizations
    \[x_D=x_1^{-a_1} x_2^{-a_2} \sum_{t=0}^{a_2}\sum_{k=0}^{a_1} \nu_{k,t} x_1^{bt}(1+x_2^c)^{a_1-k}=x_1^{-a_1} x_2^{-a_2} \sum_{s=0}^{a_1}\sum_{\ell=0}^{a_2} \theta_{s,\ell} x_2^{cs}(1+x_1^b)^{a_2-\ell},\]
    where $\nu_{k,t}$ is the number of subsets $V\subseteq_t D_2$ with $|\Sh_D(V)|=k$ and $\theta_{s,\ell}$ is the number of subsets $H\subseteq_s D_1$ with $|\Sh_D(H)|=\ell$.
    Then 
    \[\sum_{k=0}^{a_1-s} {a_1-k\choose s} \nu_{k,t}=\sum_{\ell=0}^{a_2-t} {a_2-\ell\choose t} \theta_{s,\ell}\]
    for all possible $s$ and $t$.
  \end{lemma}
  \begin{question}
    How do such expressions behave under mutations?
  \end{question}

  \begin{lemma}
    Choose $a_1,a_2\in\ZZ_{\ge0}$.
    For $D^{st}:=D_1\sqcup D_2$ with $D_2=[1,a_2]$ and $D_1=[1,a_1]+a_2$, the element $x_D$ coincides with the corresponding standard monomial basis element.
  \end{lemma}

  Our main interest will be with the following Dyck paths.
  \begin{definition}
    \label{def:dominant Dyck path}
    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, define the \emph{dominant Dyck path} $D^{dom}=D^{dom}[a_1,a_2]$ to be the maximal Dyck path starting from $(0,0)$ and terminating at $(a_1,a_2)$ while staying below the lines $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$ and $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-a_1)$.
  \end{definition}

  To understand the structure of the dominant Dyck paths, it will be convenient to consider their initial and final segments separately.
  \begin{definition}
    For $s>0$, define the \emph{Dyck path prefix} $\overrightarrow{D}^s$ as the maximal Dyck path with $s$ vertical edges starting from $(0,0)$ and terminating at $(d,s)$ while staying below the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$, where $d=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil$.
    Call this $d$ the \emph{depth} of $s$.

    For $t>0$, define the \emph{Dyck path suffix} $\overleftarrow{D}^t$ as the maximal Dyck path with $t$ horizontal edges starting from $(0,0)$ and terminating at $(t,h)$ while staying below the line $y-h=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-t)$, where $h=\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$.
    Call this $h$ the \emph{height} of $t$.
    %        y = (a2 - a1*(self._r1*self._r2-sqrt(self._r1*self._r2*(self._r1*self._r2-4)))/(2*self._r2))/(1-(self._r1*self._r2-sqrt(self._r1*self._r2*(self._r1*self._r2-4)))/(self._r1*self._r2+sqrt(self._r1*self._r2*(self._r1*self._r2-4))))
    %    corner = (y*(self._r1*self._r2-sqrt(self._r1*self._r2*(self._r1*self._r2-4)))/(2*self._r1),y)
  \end{definition}
  \begin{remark}
    There often exist multiple choices of $s$ with a given depth $d$ and multiple choices of $t$ with a given height $h$.
  \end{remark}

  The following result will be useful for showing that the Dyck path prefixes and suffixes behave properly.
  \begin{lemma}
    For $s>0$, the Dyck path prefix $\overrightarrow{D}^s$ ends in a vertical edge.
    Similarly, for $t>0$, the Dyck path suffix $\overleftarrow{D}^t$ begins with a horizontal edge.
  \end{lemma}

  Apart from being the prefix and suffix for the dominant Dyck path, the Dyck paths $\overrightarrow{D}^s$ and $\overleftarrow{D}^t$ can be observed inside the maximal Dyck paths defining cluster variables as follows.
  \begin{lemma}\mbox{}
    \begin{itemize}
      \item For $s>0$ and any $m \ge 1$ so that $s < u_{m+1,-}$, the Dyck path prefix $\overrightarrow{D}^s$ is an initial segment of the maximal Dyck path $D^{max}[u_{m,+},u_{m+1,-}]$.
      \item For $t>0$ and any $m \ge 1$ so that $t < u_{m+1,+}$, the Dyck path suffix $\overleftarrow{D}^t$ is a final segment of the maximal Dyck path $D^{max}[u_{m+1,+},u_{m,-}]$.
    \end{itemize}
  \end{lemma}

  \begin{lemma}\mbox{}
    \begin{enumerate}
      \item Choose a width $t>0$ and $a_1 \ge t$.
        Then there exists a unique $s$ of depth $a_1-t$ so that $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$ is the dominant Dyck path $D^{dom}[a_1,a_2]$ with $a_2=s+\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$.
      \item Choose a height $s>0$ and $a_2 \ge s$.
        Then there exists a unique $t$ of height $a_2-s$ so that $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$ is the dominant Dyck path $D^{dom}[a_1,a_2]$ with $a_1=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil+t$.
    \end{enumerate}
  \end{lemma}
  \begin{remark}
    The decomposition of $D^{dom}[a_1,a_2]$ as $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$ is not uniquely determined by $a_1$ and $a_2$.
    However, there exists at most two choices of $s$ and $t$ for which such a decomposition holds.
  \end{remark}

  \begin{lemma}
    \label{le:floors and ceilings}
    For any real number $x$ and any real number $r>1$, we have
    \[\lfloor x\rfloor \le \left\lfloor \lceil xr \rceil \frac{1}{r} \right\rfloor \le \lceil x\rceil \qquad \text{and} \qquad \lfloor x\rfloor \le \left\lceil \lfloor xr \rfloor \frac{1}{r} \right\rceil \le \lceil x\rceil.\]
  \end{lemma}
  \begin{proof}
    Observe that
    \[xr\le \lceil xr \rceil < xr+1 \qquad \text{and} \qquad xr-1 < \lfloor xr \rfloor \le xr\]
    and so
    \[x\le \lceil xr \rceil \frac{1}{r} < x+\frac{1}{r} \qquad \text{and} \qquad x-\frac{1}{r} < \lfloor xr \rfloor \frac{1}{r} \le x.\]
    Since $0<\frac{1}{r}<1$, the result follows.
  \end{proof}

  \begin{proposition}
    \label{prop:dominant Dyck path decomposition}
    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, the dominant Dyck path $D^{dom}[a_1,a_2]$ is the concatenation of $\overrightarrow{D}^s$ followed by $\overleftarrow{D}^t$ for any choice of $s$ and $t$ satisfying $a_2-s=\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$ and $a_1-t=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil$.
    In this case, the pair of $s$ and $t$ will be one of the following:
    \begin{align}
      \label{eq:lower bounds}
      s=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rfloor\qquad &\text{and}\qquad t=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rfloor\\
      s=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rfloor\qquad &\text{and}\qquad t=\left\lceil\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rceil\\
      \label{eq:upper bounds}
      s=\left\lceil\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rceil\qquad &\text{and}\qquad t=\left\lceil\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rceil
    \end{align}
    If two such decompositions exist, they will be of the form \eqref{eq:lower bounds} and \eqref{eq:upper bounds}.
  \end{proposition}
  \begin{remark}
    The irrationality of the slopes defining the Dyck path prefixes and suffixes makes it difficult to predict for a given choice of $a_1$ and $a_2$ precisely which of these choice of $s$ and $t$ will produce the desired equalities.
  \end{remark}
  \begin{proof}
    (In progress)

    For $s=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rfloor$, by Lemma~\ref{le:floors and ceilings} we have
    \[\left\lfloor \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rfloor \le \left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c} \right\rceil \le \left\lceil \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rceil\]
    since $0<\frac{bc-\sqrt{bc(bc-4)}}{2c}<1$.
    It follows that
    \[ a_1 - \left\lceil \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rceil \le a_1 - \left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c} \right\rceil \le a_1 - \left\lfloor \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rfloor\]
    and so
    \[ \left\lfloor \frac{ \big(bc+\sqrt{bc(bc-4)}\big) a_1 - 2 b a_2 }{2\sqrt{bc(bc-4)}} \right\rfloor \le a_1 - \left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c} \right\rceil \le \left\lceil \frac{ \big(bc+\sqrt{bc(bc-4)}\big) a_1 - 2 b a_2 }{2\sqrt{bc(bc-4)}} \right\rceil\]
    with one of these inequalities being an equality.

    If the left hand inequality is an equality, we take $t=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rfloor$.

    The desired equalities can be rewritten in the form 
    \[s=a_2-\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil=\left\lfloor a_2 - t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rfloor\]
    and
    \[t=a_1-\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil=\left\lfloor a_1 - s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rfloor.\]
    Combining these, we seek $s$ and $t$ satisfying
    \[s=\left\lfloor a_2 - \left\lfloor a_1 - s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rfloor \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rfloor\]
    and
    \[t=\left\lfloor a_1 - \left\lfloor a_2 - t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rfloor \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rfloor.\]
  \end{proof}
